Reproducible research - Peer assessments 1
=====================================================
## Loading and preprocessing the data
First, read the data in
```{r input}
dataraw <- read.csv("activity.csv", colClasses = c("numeric", "factor", "numeric"))
nrow(dataraw)
```
and then clean it up
```{r cleanup}
data <- dataraw[complete.cases(dataraw),]
nrow(data)
```
## What is mean total number of steps taken per day?
We can aggregate the data by date
```{r aggregate}
aggregatedata <- aggregate(data$steps, by = list(data$date), FUN = sum)
head(aggregatedata )
nrow(aggregatedata)
```
The histogram of the number of steps per day is
```{r hist1}
with(aggregatedata, hist(x))
```

The mean and median
```{r MeanAndMedian}
mean(aggregatedata$x)
median(aggregatedata$x)
```

## What is the average daily activity pattern?
We will need to agregate the data by minute 
```{r MinAgg}
MinAggData <- aggregate(data$steps, by = list(data$interval), FUN = sum)
```

Then the time series of the average number of steps is
```{r steps}
plot(MinAggData$Group.1, MinAggData$x, xlab = "minute interval", ylab = "average number of steps", type = 'l')
```
The row index of the 5 minute interval that has maximum number of steps is
```{r maxstep}
which.max(MinAggData$x)
```
## Imputing missing values
The total number of missing data
```{r missing data}
nrow(dataraw) - nrow(data)
```

## Are there differences in activity patterns between weekdays and weekends?
